Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-02-11 mice_synthesizing/paper.Rmd
Add imputation procedure.

By default, `mice` imputes all values that are coded as missing in the dataset. However, using the `where` parameter within the `mice`-function, one can choose to impute any value in the dataset. As input, the `where` parameter requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logicals $z_{jk}$ that indicate which cells are selected to have their values replaced. This approach allows to overimpute a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values.

>>>>

By default, `mice` imputes all values that are coded as missing in the dataset. However, using the `where` parameter within the `mice`-function, one can choose to impute any value in the dataset. As input, the `where` parameter requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logicals $z_{jk}$ that indicate which cells are selected to have their values replaced. This approach allows to *overimpute* a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values. Other parameters that are required to be specified are the number of imputations $m$ (`m`), the imputation method (`method`), and the predictor matrix, specifying the predictor variables that are used in the imputation model for every variable $j$ that has some of its values replaced (`predictorMatrix`).

Discuss CART (read Reiter)
Add text about additional CART parameters cp and minbucket
